---
title: "EcoData - A collection of ecological datasets for teaching"
author: "Florian Hartig, Theoretical Ecology, University of Regensburg [website](http://www.uni-regensburg.de/biologie-vorklinische-medizin/theoretische-oekologie/mitarbeiter/hartig/)"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{EcoData - A collection of ecological datasets for teaching}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
abstract: "EcoData is a collection of ecological datasets for teaching"
---

```{r, echo = F}
library(EcoData)
```


```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=7, fig.height=4.5, fig.align='center', warning=FALSE, message=FALSE, cache = F)
```

# Datasets according to use

## Tests

### t-test

* datasets::PlantGrowth -> discrete predictors (3 treatments)
* EcoData::regrowth -> discrete predictors (2 treatments)

### ANOVA

* datasets::PlantGrowth -> discrete predictors (1 predictor, 3 treatments)

## Regression

### Linear regression

* EcoData::solomonislands -> continous predictors (count data, but can be used with linear regression)
* datasets::airquality -> mostly continous predictors
* datasets::PlantGrowth -> discrete predictors (3 treatments)
* EcoData::wine -> continous predictors
* EcoData::regrowth -> discrete predictors (2 treatments)

### GLM

#### Poisson

* EcoData::birdfeeding 
* EcoData::solomonislands 
* EcoData::volcanoisland 

#### Logistic regression

* EcoData::titanic 
* EcoData::nasa 
* EcoData::volcanoisland 
* datasets::esoph 
* boot::melanoma

### GLMM 

EcoData::volcanoisland -> Random Effects, zero-inflation, spatial effects
glmmTMB::owls -> Random Effects, zero-inflation
boot::nitrofen -> Poisson -> logistic with RE (1|individual)
DHARMa::hurricanes -> Poisson / NB, model selection, ... 

## MachineLearning

* EcoData::dataset_flower() -> Image Recognition
* EcoData::titanic_ml -> Classification 

### Classification

* datasets::iris



