---
title: "EcoData - A collection of ecological datasets for teaching"
author: "Florian Hartig, Theoretical Ecology, University of Regensburg [website](http://www.uni-regensburg.de/biologie-vorklinische-medizin/theoretische-oekologie/mitarbeiter/hartig/)"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Vignette for the EcoData package}
  %\VignetteEngine{knitr::knitr}
  %\VignetteEncoding{UTF-8}
abstract: "EcoData is a collection of ecological datasets for teaching"
---

```{r, echo = F}
library(EcoData)
```


```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=7, fig.height=4.5, fig.align='center', warning=FALSE, message=FALSE, cache = F)
```

# Datasets according to use

## Tests

### t-test

* datasets::PlantGrowth -> discrete predictors (3 treatments)
* EcoData::regrowth -> discrete predictors (2 treatments)

### ANOVA

* datasets::PlantGrowth -> discrete predictors (3 treatments)


## Regression

### Linear regression

* EcoData::solomonislands -> continous predictors (count data, but can be used with linear regression)
* datasets::airquality -> mostly continous predictors
* datasets::PlantGrowth -> discrete predictors (3 treatments)
* EcoData::regrowth -> discrete predictors (2 treatments)

### GLM


* EcoData::birdfeeding -> Poisson 
* EcoData::solomonislands -> Poisson
* EcoData::volcanoisland -> Poisson, Logistic
* EcoData::titanic -> Logistic 1/0
* datasets::esoph -> Logistic, k/n


### GLMM 

* EcoData::volcanoisland -> Random Effects, zero-inflation, spatial effects
* glmmTMB::owls -> Random Effects, zero-inflation

## MachineLearning

### Classification

* datasets::iris



